\documentclass{article}
\usepackage[pdftex]{hyperref}
\usepackage{multicol}

% LAST UPDATED: 2023-06-15

% ***************************************************************************
% Page style and formatting options
% ***************************************************************************

% This is to make the margins look nice for 8.5x11 paper, 1 inch border on left, rigth, and top and 1 inch between 
% bottom of text and bottom of paper, but .5 inch between bottom of footer and bottom of paper.

%\usepackage{fullpage} % fixes the annoyingly large default margins. 
\setlength{\textwidth}{6.7in}
\setlength{\oddsidemargin}{-0.10in}
\setlength{\evensidemargin}{0in}
\setlength{\topmargin}{-.4in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0.4in}
\setlength{\textheight}{9.3in}
\setlength{\footskip}{0.2in}

\setlength{\topskip}{0in}       % No blank space on first page
%\setcounter{\secnumdepth}{0}     % Turn of section numbering
\setlength{\parindent}{0in}     % I hate indented paragraphs
\setlength{\parskip}{0.1in}

% ***************************************************************************
% Generic header and title info
% ***************************************************************************

\newcommand{\myname}{Catalina Medina}
\newcommand{\myemail}{\href{mailto:catalmm1@uci.edu}{catalmm1@uci.edu}}

\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancy}
\lhead{\myemail} 
\chead{\myname}
\rhead{\thepage/\pageref*{LastPage}}
\cfoot{} % remove default page numbering 


% ************************************************************************
% ************************************************************************
%
%              Here's where the actual document begins.
%
% ************************************************************************
% ************************************************************************
\begin{document}
	\thispagestyle{empty}
	\phantom{.}\vspace{-2cm}
	\begin{center}
		{\huge \bf \myname}\\
		Email: \myemail\\
		GitHub: \href{https://github.com/CatalinaMedina}{CatalinaMedina}
		%\large \bf \myemail \\
		%\emph{Last updated {\today}.}
	\end{center}
	%\vspace{-5mm}
	%\begin{minipage}[t]{3in}
	%	\myhomeaddress \\
	%\end{minipage}
	%\hfill
	%\begin{minipage}[t]{3in}
	%	\begin{tabbing}
		%		\myworkaddress \newline\\
		%	\end{tabbing}
	%\end{minipage}
	
	\vspace{-4mm}
	\rule{\linewidth}{1pt}
	
	% ************************************************************************
	%                     Start Filling in Stuff below here
	% ************************************************************************
	
	\begin{description}
		\vspace{-2mm}
		\item[Research Interests]\hspace*{.1in}
		
		Statistics and data science education research promoting student engagement with open access materials.
		
		Bayesian statistics and epidemiological applications of statistics to better understand disease and infection, especially through collaborations with public health researchers.
		%        \vspace{-2mm}
		%        \begin{multicols}{2}
			%            Statistics and data science education\\
			%           Bayesian statistics\\
			%            Epidemiological applications\\
			%            Public health collaborations
			%        \end{multicols}
	\end{description}
	
	\vspace{-2mm}
	\rule{\linewidth}{1pt}
	
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	
	\begin{description}
		\vspace{-2mm}
		\item[Education]\hspace*{.1in}
		
		\textbf{PhD, Statistics} \hfill{Jun. 2025 (Expected)} \\
		Co-advisored by: Volodymyr Minin and Mine Dogucu\\	
		University of California, Irvine
		\vspace*{1mm}
		
		\textbf{MS, Statistics}\hfill{Jun. 2021}\\
		University of California, Irvine
		\vspace*{1mm}
		
		\textbf{BS, Mathematics} with specialization in Statistics and Minor in Biology \hfill{May 2019} \\
		University of Nevada, Reno
		
	\end{description}
	\vspace{-2mm}
	\rule{\linewidth}{1pt}
	
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	
	\begin{description}
		\vspace{-2mm}
		\item[Teaching Experience]\hspace*{.1in} 
		
		\textbf{Instructor of Record} - UC Irvine\\
		\textit{Designed and taught an introductory five-week course with a teaching assistant.}
		\begin{itemize}
			\item Basic Statistics (Stats 7) \hfill{Summer 2022}\\
			40 undergraduate students
		\end{itemize}
		
		\textbf{Instructor of Record} - University of Nevada, Reno\\
		\textit{Taught two remedial five-week courses without a teaching assistant.}
		\begin{itemize}
			\item Elementary Algebra (Math 95) \hfill{Summer 2019}\\
			25 undergraduate students
			
			\item Intermediate Algebra (Math 96) \hfill{Summer 2019}\\
			25 undergraduate students
		\end{itemize}			
		
		\textbf{Teaching Assistant} - UC Irvine\\
		\textit{Responsibilities included preparing and running weekly hour-long discussion/lab sessions and holding office hours, for two sections per class.}
		\begin{itemize}
			\item Introduction to Probability and Statistics I (Stats 120A)\hfill{Fall 2022}\\
			43 undergraduate students
			
			\item Statistical Methods for Data Analysis I (Stats 110)\hfill{Summer 2021}\\
			77 undergraduate and graduate students %37 and 40
			
			\item Introduction to Probability and Statistics (Stats 120A)\hfill{Summer 2020}\\
			77 undergraduate students %41 + 36 students			
			
			\item Introduction to Probability and Statistics for Computer Science (Stats 67) \hfill{Spring 2020}\\
			119 undergraduate students %60 students and 59
			
			\item Statistical Methods for Data Analysis II (Stats 111) \hfill{Winter 2020}\\
			99 undergraduate and graduate students %50 and 49 students
			
			\item Introduction to Biological Statistics (Stats 8) \hfill{Fall 2019}\\
			88 undergraduate students %55 and 33 students
		\end{itemize}
		
	\end{description}
	\vspace{-2mm}
	\rule{\linewidth}{1pt}
	
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	
	\begin{description}
		\vspace{-2mm}
		\item[Teaching Preparation]\hspace*{.1in}
		
		California State University Pre-Professor Program Fellow \hfill{Fall 2024}\\
		Graduate Division, UC Irvine 
		\vspace*{1mm}
		
		%Do I add Mine's statistics and data science education research group?
		
		Preparing for Careers in Teaching Statistics and Data Science Workshop \hfill{Fall 2024}\\
		Section on Statistics and Data Science Education, American Statistical Association 
		\vspace*{1mm}
		
		Summer Teaching Apprenticeship Program Fellow \hfill{Summer 2022}\\
		Division of Teaching Excellence and Innovation, UC Irvine
		\vspace*{1mm}
		
	\end{description}
	\vspace{-2mm}
	\rule{\linewidth}{1pt}
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	
	
	\begin{description}
		\vspace{-2mm}
		
		\item[Manuscripts] \hspace*{.1in} 
		
		\textbf{Peer-Reviewed Publications}
		
		\setlength{\leftskip}{0.5cm}
		
		Ricci, F., \textbf{Medina, C. M}, \& Dogucu, M. (2024). Designing and implementing an automated grading workflow for providing personalized feedback to open-ended data science assignments. \textit{Technology Innovations in Statistics Education}, 15(1).
		\vspace*{1mm}
		
		Parker, D.M., \textbf{Medina, C.}, Bohl, J., Lon, C., Chea, S., Lay, S., Kong, D., Nhek, S., Man, S., Doehl, J.S.P., Leang, R., Kry, H., Rekol, H., Oliveira, F., Minin, V.M., Manning, J.E. (2023). Determinants of exposure to Aedes mosquitoes: a comprehensive geospatial analysis in peri-urban Cambodia. \textit{Acta Tropica}, 239, 106829. 
		\vspace*{1mm}
		
		Parker, D.M., Bruckner, T., Vieira, V.M., \textbf{Medina, C.}, Minin, V.N., Felgner, P.L., Dratch, A., Zahn, M., Bartell, S.M. and Boden-Albala, B. (2021). Predictors of test positivity, mortality, and seropositivity during the early coronavirus disease epidemic, Orange County, California, USA. \textit{Emerging infectious diseases}, 27(10), 2604.
		\vspace*{1mm}
		
		\setlength{\leftskip}{0cm}
		
		\textbf{Under preparation / Pre-prints}
		%APA format
		
		\setlength{\leftskip}{0.5cm}
		
		[Submitted] \textbf{Medina, C. M.}, Palacios, J. A., Minin, V. M. (2024+). Accounting for reporting delays in real-time phylodynamic analyses with preferential sampling.\\
		\url{https://arxiv.org/abs/2407.18432}
		\vspace*{1mm}
		
		[In revisions] Dogucu, M., Demirci, S., Bendekgey, H., Ricci F. Z.,\& \textbf{Medina, C. M.} (2024+). Undergraduate data science education: Who has the microphone and what are they saying?\\
		\url{https://doi.org/10.48550/arXiv.2403.03387}
		\vspace*{1mm}
		
	\end{description}
	\vspace{-2mm}
	\rule{\linewidth}{1pt}
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	
	\begin{description}
		\vspace{-2mm}
		\item[Awards]\hspace*{.1in}
		
		Excellence in Research Award\hfill{2023}\\
		Latino Excellence and Achievement, Donald Bren School of ICS, UC Irvine
		\vspace*{1mm}
		
		Conference Travel Award \hfill{2022 \& 2018}\\
		National Diversity in STEM Conference, Society for the Advancement of Chicanos/Hispanics and Native Americans in Science (SACNAS)
		\vspace*{1mm}
		
		Outstanding Graduate Teaching Assistant Award \hfill{2020}\\ 
		Department of Statistics, UC Irvine
		\vspace*{1mm}
		
		Undergraduate Research Award\hfill{2019}\\
		University of Nevada, Reno
		\vspace*{1mm}
		
		Prize for Undergraduate Research in Quantitative Biology (Runner-up)\hfill{2018}\\
		NSF-Simons Center for Quantitative Biology, Northwestern University
		\vspace*{1mm}
		
		Capstone Conference Travel Award\hfill{2018}\\
		Mathematical Biosciences Institute, Ohio State University
		
	\end{description}
	\vspace{-2mm}
	\rule{\linewidth}{1pt}
	
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	
	
	\begin{description}
		\vspace{-2mm}
		\item[Conference Presentations]\hspace*{.1in}
		
		\textbf{Accounting for reporting delays in real-time inference of infectious diseases dynamics using pathogen genetic sequences}
		\begin{itemize}
			\item \textit{SACNAS National Diversity in STEM (NDiSTEM) Conference}\hfill{Oct. 2024}\\
			Session: (Bio)statistics: Facilitating biomedical discoveries and public health decision making\\
			Talk \& session organizer, Phoenix, AZ
			
			\item \textit{Joint Statistical Meeting (JSM)}\hfill{Aug. 2024}\\
			Speed talk \& poster presentation, Portland, OR
			
			\item \textit{Statistical and Machine Learning Applications in Biomedical Sciences Workshop}\hfill{Feb. 2024}\\
			Poster, UC Irvine
			
			\item \textit{SACNAS National Diversity in STEM (NDiSTEM) Conference}\hfill{Oct. 2022}\\ 
			Poster, San Juan, Puerto Rico 
		\end{itemize}
		
		\textbf{Automate your grading workflow with gradetools: a grading assistant in RStudio}
		\begin{itemize}
			\item \textit{Electronic Conference on Teaching Statistics (eCOTS) Regional}\hfill{Jun. 2024}\\
			Flash talk, UC Irvine
			
			\item \textit{United States Conference on Teaching Statistics (USCOTS)}\hfill{Jun. 2023}\\
			Workshop, State College, PA
			
			\item \textit{Researchers of Statistics Education (ROSE) Conference}\hfill{May 2023}\\
			Invited presentation, online
		\end{itemize}
		
		\textbf{Building data science education research plan for teacher-scholars}
		\begin{itemize}
			\item \textit{Electronic Conference On Teaching Statistics (eCOTS)}\hfill{Jun. 2023}\\
			Breakout session, selected as "hot topic of the day", online
		\end{itemize}
		
		\textbf{Determinants of exposure to Aedes mosquitoes: a comprehensive geospatial analysis in peri-urban Cambodia}
		\begin{itemize}
			\item \textit{GEOMED: Interdisciplinary Conference on Spatial Statistics, Spatial Epidemiology, and Geographical Aspects of Public Health}\hfill{Oct. 2022}\\
			Poster, UC Irvine
		\end{itemize}
		
		\textbf{Host-pathogen dynamics: Quantifying process-level variation using a system-specific dynamical model in a non-linear mixed effects modeling framework}
		\begin{itemize}
			\item \textit{College of Science Poster Session}\hfill{Nov. 2018}\\
			Poster, University of Nevada, Reno 
			
			\item \textit{Conference on Quantitative Approaches in Biology} \hfill{Nov. 2018}\\
			Poster, Northwestern University 
			
			\item \textit{SACNAS National Diversity in STEM (NDiSTEM) Conference}\hfill{Oct. 2018}\\ 
			Poster, San Antonio, TX
			
			\item \textit{McNair Symposium}\hfill{Aug. 2018}\\
			Talk, University of Nevada, Reno 
			
			\item \textit{Mathematical Biosciences Institute Capstone Conference}\hfill{Aug. 2018}\\
			Poster, Ohio State University
			
			\item \textit{National McNair Conference}\hfill{Jul. 2018}\\
			Talk, University of California, Los Angeles
		\end{itemize}
		
	\end{description}
	\vspace{-2mm}
	\rule{\linewidth}{1pt}
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	
	\newpage
	\begin{description}
		\vspace{-2mm}
		\item[Professional Service and Outreach]\hspace*{.1in} 
		
		Graduate student representative, UC Irvine Statistics Department\hfill{Fall 2021 - Spring 2024}
		\vspace*{-2mm}
		\begin{itemize}
			\item Organized and led visitation day for admitted PhD students
			\vspace*{-1mm}
			\item Founded, organized, and led orientation for first year graduate students
			\vspace*{-1mm}
			\item Reported on graduate student matters at weekly faculty meetings
			\vspace*{-1mm}
		\end{itemize}
		\vspace*{1mm}
		
		Panel moderator: What's Next in Four-Year Institutions?\hfill{Jun. 2024}\\
		\textit{Electronic Conference on Teaching Statistics Regional}, UC Irvine 
		\vspace*{1mm}
		
		Panelist: Societal and Ethical Issues in Computational and Informational Sciences\hfill{Apr. 2023}\\ 
		Diverse Educational Community and Doctoral Experience, UC Irvine
		\vspace*{1mm}
		
		Creator of animated maps to visualize Orange County COVID-19 cases, tests, and percent positivity by zip code for the public\hfill{2021}\\
		COVID-19 Trends by UC Irvine \url{https://www.stat.uci.edu/covid19/index.html}
		\vspace*{1mm}
		
		Panelist: Careers for mathematics, physics, and atmospheric science majors\hfill{Nov. 2020}\\
		First-year seminar, University of Nevada, Reno
		\vspace*{1mm}
		
		Panelist: Graduate school\hfill{Nov. 2020}\\
		Association for Women in Mathematics, University of Nevada, Reno
		\vspace*{1mm}
		
		Invited presentation: My early graduate school experience and life at UC Irvine\hfill{Dec. 2020}\\
		McNair Scholars University of Nevada, Reno
		
	\end{description}
	\vspace{-2mm}
	\rule{\linewidth}{1pt}
	
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	
	
	\begin{description}
		\vspace{-2mm}
		\item[Mentoring]\hspace*{.01in}
		
		Competitive Edge Summer Research Program mentor \hfill{Summer 2023}\\
		Graduate Division, UC Irvine 
		\vspace*{1mm}
		
		Mentoring Excellence Certificate \hfill{Summer 2023}\\
		Graduate Division, UC Irvine
		\vspace*{1mm}
		
		First year statistics graduate student mentor\hfill{2021 - 2023}\\
		Diverse Educational Community and Doctoral Experience, UC Irvine
		
	\end{description}
	\vspace{-2mm}
	\rule{\linewidth}{1pt}
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	
	
	\begin{description}
		\vspace{-2mm}
		\item[Programs and Professional Membership]\hspace*{.01in}
		
		American Statistical Association
		
		Society for the Advancement of Chinanos/Hispanics and Native Americans in Science (SACNAS)
		
		2018-2019 McNair Scholar at University of Nevada, Reno
		
	\end{description}
	\vspace{-2mm}
	\rule{\linewidth}{1pt}
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	
	\begin{description}
		\vspace{-2mm}
		\item[Software Developed]\hspace*{.1in}
		
		\texttt{phylodyn2} R package for viral phylodynamic inference with ability to account for reporting delays in real-time analyses with preferential sampling. \url{https://github.com/CatalinaMedina/phylodyn2}
		
		\texttt{gradetools} R package to help automate grading workflows and facilitate in creating individualized assignment feedback for students. (\textit{co-developer}) \url{https://federicazoe.github.io/gradetools/}
		
	\end{description}
	\vspace{-2mm}
	\rule{\linewidth}{1pt}
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	
	\begin{description}
		\vspace{-2mm}
		\item[Certifications]\hspace*{.01in}
		
		Summer Institute in Statistics and Modeling in Infectious Diseases (SISMID), University of Washington
		\vspace*{-1mm}
		
		\begin{itemize}
			\item Certification in Stochastic Epidemic Models with Inference  \hfill{2021}
			\item Certification in MCMC II for Infectious Diseases \hfill{2021}
			\item Certification in Evolutionary Dynamics and Molecular Epidemiology of Viruses \hfill{2021}
		\end{itemize}
	\end{description}
	\vspace{-2mm}
	\rule{\linewidth}{1pt}
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	
	
\end{document}
